### 2020-06-05 writeup/experiments.tex
sec 4

Our first result is to show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
Over six randomly selected task pairs from the sentiment analysis dataset, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

@@

A common challenge in the study of multi-task learning is that the results can be hard to understand.
It is difficult to predict when MTL performs well without running extensive trials.
Our insight here is that we can use STL results to help understand MTL results.
We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
The results show that STL results are indicative of MTL results.

>>>>

\textit{Predicting transfer effect via STL results.}
We show that the single-task based metric proposed in Section \ref{sec_similarity} can predict positive or negative transfer in MTL.
A common challenge in the study of multi-task learning is that the results can be hard to understand.
It is difficult to predict when MTL performs well without running extensive trials.
Our insight here is that we can use STL results to help understand MTL results.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 tasks.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among $30$ times $5$ (random seeds) task pairs!
We observe similar results for $91$ task pairs from the ChestX-ray14 dataset.
%The results show that STL results are indicative of MTL results.

\textit{Mitigating negative transfer via incremental training.}
Our show that our proposed incremental training schedule (Algorithm \ref{alg_inc_train}) can help mitigate negative transfer for predicting a particular target task.
Our insight is that since adding more samples from the source task does not always improve performance, we can improve efficiency by adding the source samples \textit{incrementally} during training.
Over six randomly selected task pairs from the sentiment analysis dataset, we find that Algorithm \ref{alg_inc_train} requires only $45\%$ of the computational cost to achieve the same performance on the target task, compared to the multi-task learning baseline.

@@

### 2020-06-05 writeup/related.tex
sec 4

>>>>

In this work, we analyzed the bias and variance of multi-task learning versus single-task learning.
We provided tight concentration bounds for the bias and the variance.
Based on these bounds, we analyzed the impact of three properties, including task similarity, sample data and covariate shift on the bias and variance, to derive conditions where MTL performs better than STL.
%Each of these results (based on each of the 3 properties) gives a different algorithmic/practical insight.
We validated our theoretical results.
Based on the theory, we proposed to train multi-task models by incrementally adding labeled data and showed that our proposed method outperforms baseline multi-task training on sentiment analysis tasks.
We described several open questions for future work.
First, our result on the bias of multi-task learning (cf. Lemma \ref{lem_cov_derivative}) involves an error term that scales down with $\rho_1$.
Tightening this error bound can potentially cover the unexplained observations in Figure \ref{fig_model_shift_phasetrans}.
Second, it would be interesting to extend our results to non-linear settings.
This likely requires addressing significant technical challenges in order to deal with non-linearity.
